PANCHANGE_analysis

### 2021-03-09 PANCHANGE_analysis.Rmd
renamed explanatory variables for disorder symptoms prepandemic
reordered Prepandemic and retrospective predictors to match legend

lin_preds <- c("time_diff_coping_lockdown_march_23",
               "GAD.prepandemic",
               "PHQ.prepandemic",
               "PCL.prepandemic",
               "GAD.retrospective",
               "PHQ.retrospective",
               "PCL.retrospective"
               )

@@

>>>>

lin_preds <- c("time_diff_coping_lockdown_march_23",
               "GAD.prepandemic",
               "PCL.prepandemic",
               "PHQ.prepandemic",
               "GAD.retrospective",
               "PCL.retrospective",
               "PHQ.retrospective"
               )

@@

plot.dat.disorder <- plot.dat.disorder %>%
  mutate(RowLabels = recode(RowLabels,
                            `PCL.prepandemic` = "PCL total prepandemic",
                            `PHQ.prepandemic` = "PHQ total prepandemic",
                            `GAD.prepandemic` = "GAD total prepandemic"
                            ))
